---
title: "MUSA 508 Final - Amsterdam"
author: 'Ben Keel, Yuhao Sun & Ann (Zian) Zhang'
date: "2022/12/06"
output: 
  html_document:
    theme: lumen
    toc: true
    toc_float: true
    toc_collapsed: true
    code_folding: hide
---

```{r setup, include=FALSE, message = FALSE,warning = FALSE, echo = FALSE}
knitr::opts_chunk$set(echo = TRUE, quiet = TRUE, warning=FALSE)
```

# Presentation - Youtube Link

# Background Information -- Amsterdam Airbnb Market

(embed several photos?)

# Data Source

```{r Load R packages, include=TRUE, echo = TRUE, message = FALSE, warning = FALSE}

source("https://raw.githubusercontent.com/urbanSpatial/Public-Policy-Analytics-Landing/master/functions.r")

library(tidyverse)
library(sf)
library(RSocrata)
library(viridis)
library(spatstat)
library(ggplot2)
library(raster)
library(spdep)
library(FNN)
library(mapview)
library(grid)
library(gridExtra)
library(knitr)
library(stringr)
library(kableExtra)
library(tidycensus)
library(lubridate)
library(viridis)
library(stargazer)
library(dplyr)
library(plyr)

library(scales)
library(RColorBrewer)
library(gridExtra)
library(ggthemes)
library(readr)
library(ggcorrplot)
library(caret)

library(sjPlot)
library(sjmisc)
library(sjlabelled)
library(osmdata)

#text mining
library(tm)
library(wordcloud2)
library(SnowballC)
options(scipen=999)
```

```{r formatting, include=FALSE, echo = TRUE, message = FALSE, warning = FALSE}

palette5 <- c("#FA8072","#9FE2BF","#FF006A","#FE4C35","#FE9900")
palette4 <- c("#FA8072","#9FE2BF","#FE4C35","#FE9900")
palette2 <- c("#FA8072","#9FE2BF")
Teal <- c("#d1eeea", "#a8dbd9", "#85c4c9", "#68abb8", "#4f90a6")
Purple <- c("#f3e0f7", "#e4c7f1", "#d1afe8", "#b998dd", "#9f82ce")
Pink <- c("#ffffff","#f9f4f4","#f0e4e4", "#e7d3d3", "#dec3c3")

qBr <- function(df, variable, rnd) {
  if (missing(rnd)) {
    as.character(quantile(round(df[[variable]],0),
                          c(.01,.2,.4,.6,.8), na.rm=T))
  } else if (rnd == FALSE | rnd == F) {
    as.character(formatC(quantile(df[[variable]]), digits = 3),
                 c(.01,.2,.4,.6,.8), na.rm=T)
  }
}

qBr2 <- function(df, variable, rnd) {
  if (missing(rnd)) {
    as.character(round(quantile(round(df[[variable]],0),
                          c(.01,.2,.4,.6,.8), na.rm=T)))
  } else if (rnd == FALSE | rnd == F) {
    as.character(round(formatC(quantile(round(df[[variable]]), 0)),
                 c(.01,.2,.4,.6,.8), na.rm=T))
  }
}

q5 <- function(variable) {as.factor(ntile(variable, 5))}

plotTheme <- function(base_size = 12) {
  theme(
    text = element_text( color = "black"),
    plot.title = element_text(size = 14,colour = "black"),
    plot.subtitle = element_text(face="italic"),
    plot.caption = element_text(hjust=0),
    axis.ticks = element_blank(),
    panel.background = element_blank(),
    panel.grid.major = element_line("grey80", size = 0.1),
    panel.grid.minor = element_blank(),
    panel.border = element_rect(colour = "black", fill=NA, size=2),
    strip.background = element_rect(fill = "grey80", color = "white"),
    strip.text = element_text(size=12),
    axis.title = element_text(size=12),
    axis.text = element_text(size=10),
    plot.background = element_blank(),
    legend.background = element_blank(),
    legend.title = element_text(colour = "black", face = "italic"),
    legend.text = element_text(colour = "black", face = "italic"),
    strip.text.x = element_text(size = 14)
  )
}

mapTheme <- theme(plot.title =element_text(size=12),
                  plot.subtitle = element_text(size=8),
                  plot.caption = element_text(size = 8),
                  axis.line=element_blank(),
                  axis.text.x=element_blank(),
                  axis.text.y=element_blank(),
                  axis.ticks=element_blank(),
                  axis.title.x=element_blank(),
                  axis.title.y=element_blank(),
                  panel.background=element_blank(),
                  panel.border = element_rect(colour = "black", fill=NA, size=2),
                  panel.grid.major=element_line(colour = 'grey92'),
                  panel.grid.minor=element_blank(),
                  legend.direction = "vertical", 
                  legend.position = "right",
                  plot.margin = margin(1, 1, 1, 1, 'cm'),
                  legend.key.height = unit(1, "cm"), legend.key.width = unit(0.2, "cm"))

```

```{r function, include=FALSE, echo = TRUE, message = FALSE, warning = FALSE}
nn_function <- function(measureFrom,measureTo,k) {
  measureFrom_Matrix <- as.matrix(measureFrom)
  measureTo_Matrix <- as.matrix(measureTo)
  nn <-   
    get.knnx(measureTo, measureFrom, k)$nn.dist
  output <-
    as.data.frame(nn) %>%
    rownames_to_column(var = "thisPoint") %>%
    gather(points, point_distance, V1:ncol(.)) %>%
    arrange(as.numeric(thisPoint)) %>%
    group_by(thisPoint) %>%
    summarize(pointDistance = mean(point_distance)) %>%
    arrange(as.numeric(thisPoint)) %>% 
    dplyr::select(-thisPoint) %>%
    pull()
  
  return(output)  
}


rquery.wordcloud <- function(x, type=c("text", "url", "file"), 
                          lang="english", excludeWords=NULL, 
                          textStemming=FALSE,  colorPalette="Dark2",
                          min.freq=3, max.words=200)
{ 
  library("tm")
  library("SnowballC")
  library("wordcloud")
  library("RColorBrewer") 
  
  if(type[1]=="file") text <- readLines(x)
  else if(type[1]=="url") text <- html_to_text(x)
  else if(type[1]=="text") text <- x
  
  # Load the text as a corpus
  docs <- Corpus(VectorSource(text))
  # Convert the text to lower case
  docs <- tm_map(docs, content_transformer(tolower))
  # Remove numbers
  docs <- tm_map(docs, removeNumbers)
  # Remove stopwords for the language 
  docs <- tm_map(docs, removeWords, stopwords(lang))
  # Remove punctuations
  docs <- tm_map(docs, removePunctuation)
  # Eliminate extra white spaces
  docs <- tm_map(docs, stripWhitespace)
  # Remove your own stopwords
  if(!is.null(excludeWords)) 
    docs <- tm_map(docs, removeWords, excludeWords) 
  # Text stemming
  if(textStemming) docs <- tm_map(docs, stemDocument)
  # Create term-document matrix
  tdm <- TermDocumentMatrix(docs)
  m <- as.matrix(tdm)
  v <- sort(rowSums(m),decreasing=TRUE)
  d <- data.frame(word = names(v),freq=v)
  # check the color palette name 
  if(!colorPalette %in% rownames(brewer.pal.info)) colors = colorPalette
  else colors = brewer.pal(8, colorPalette) 
  # Plot the word cloud
  set.seed(1234)
  wordcloud(d$word,d$freq, min.freq=min.freq, max.words=max.words,
            random.order=FALSE, rot.per=0.35, 
            use.r.layout=FALSE, colors=colors)
  
  invisible(list(tdm=tdm, freqTable = d))
}
#++++++++++++++++++++++
# Helper function
#++++++++++++++++++++++
# Download and parse webpage
html_to_text<-function(url){
  library(RCurl)
  library(XML)
  # download html
  html.doc <- getURL(url)  
  #convert to plain text
  doc = htmlParse(html.doc, asText=TRUE)
 # "//text()" returns all text outside of HTML tags.
 # We also don’t want text such as style and script codes
  text <- xpathSApply(doc, "//text()[not(ancestor::script)][not(ancestor::style)][not(ancestor::noscript)][not(ancestor::form)]", xmlValue)
  # Format text vector into one character string
  return(paste(text, collapse = " "))
}
```

```{r load data, include=FALSE, echo = TRUE, message = FALSE, warning = FALSE}

#listings <- st_read("listings.csv")
#details <- st_read("listings_details.csv")
#calendar <- read.csv("calendar.csv")


details <- read.csv("/Users/annzhang/Downloads/archive/listings_details.csv")
listings <- read.csv("/Users/annzhang/Downloads/archive/listings.csv")
calendar <- read.csv("/Users/annzhang/Downloads/archive/calendar.csv")


#large neighborhood
neighborhood <- st_read('neighbourhoods.geojson')

#small neighborhood
neighbor2 <- st_read('neighbor2.json') %>% 
  st_transform(st_crs(neighborhood))

developing_area <- st_read('developing_area.json') %>% 
  st_transform(st_crs(neighborhood))

crowdsensor <- st_read('crowdsensor.json') %>% 
  st_transform(st_crs(neighborhood))

metro <- st_read('tram_metro_stops.json') %>% 
  st_transform(st_crs(neighborhood))

buildingyear <- st_read('buildingyearblock.json') %>% 
  st_transform(st_crs(neighborhood))

zipcode6 <- st_read('zipcode6.json') %>% 
  st_transform(st_crs(neighborhood))

zipcode4 <- st_read('zipcode4.json') %>% 
  st_transform(st_crs(neighborhood))
```

```{r  text, include=TRUE, echo = TRUE, message = FALSE, warning = FALSE}
details.sf <- st_as_sf(details,coords = c('longitude','latitude'),crs = 4326) %>% 
  st_transform(st_crs(neighborhood))

details.sf$price <- parse_number(details.sf$price)
details.sf$weekly_price <- parse_number(details.sf$weekly_price)
details.sf$monthly_price <- parse_number(details.sf$monthly_price)
details.sf$cleaning_fee <- parse_number(details.sf$cleaning_fee)
details.sf$extra_people <- parse_number(details.sf$extra_people)
details.sf$security_deposit <- parse_number(details.sf$security_deposit)
details.sf$beds <- as.numeric(details.sf$beds)
details.sf$minimum_nights <- as.numeric(details.sf$minimum_nights)
details.sf$maximum_nights <- as.numeric(details.sf$maximum_nights)
details.sf$number_of_reviews <- as.numeric(details.sf$number_of_reviews)
details.sf$review_scores_rating <- as.numeric(details.sf$review_scores_rating)
details.sf$review_scores_accuracy <- as.numeric(details.sf$review_scores_accuracy)
details.sf$review_scores_cleanliness<- as.numeric(details.sf$review_scores_cleanliness)
details.sf$review_scores_value <- as.numeric(details.sf$review_scores_value)
details.sf$reviews_per_month <- as.numeric(details.sf$reviews_per_month)
details.sf$id <- as.character(details.sf$id)
details.sf$property_type <- as.factor(details.sf$property_type)

details.sf.raw <- details.sf
```

# Exploratory Analysis

```{r price panel, include=TRUE, echo = TRUE, message = FALSE, warning = FALSE}
# Available Calendar
available_calendar <- calendar %>%
  filter(available =="t")

available_calendar$listing_id <- as.character(available_calendar$listing_id)

# Price change
available_calendar <- available_calendar%>%
  mutate(price2 = gsub("^.","",price))%>%
  mutate(price2 = gsub(",","",price2))

available_calendar$price3 <- as.numeric(available_calendar$price2)

# Sum per month
available_calendar2 <- available_calendar%>%
  mutate(date2 = ymd(date))%>%
  mutate(month = month(date2))%>%
  group_by(listing_id, month) %>%
  dplyr::summarize(month_price = mean(price3))
```

```{r panel length, include=TRUE, echo = TRUE, message = FALSE, warning = FALSE}
length(unique(calendar$listing_id))
length(unique(calendar$listing_id))*12
```

```{r deal with panel, include=TRUE, echo = TRUE, message = FALSE, warning = FALSE}
study.panel <- 
  expand.grid(listing_id = unique(calendar$listing_id),
              month=unique(available_calendar2$month))
study.panel$listing_id <- as.character(study.panel$listing_id)
listing_panel <- study.panel %>%
  left_join(available_calendar2) %>%
  mutate(each_month_price = 0)
o <- order(listing_panel[,"listing_id"],listing_panel[,"month"])
listing_panel <- listing_panel[o,]
xx <- 0
for(i in 2:nrow(listing_panel)){
  if(!is.na(listing_panel[i,3])){
    xx <- listing_panel[i,3]
    listing_panel[i,4]=listing_panel[i,3]
  }
  if(is.na(listing_panel[i,3])& listing_panel[i-1,1]==listing_panel[i,1]){
    listing_panel[i,4] <- xx
  }
  if(is.na(listing_panel[i,3])& listing_panel[i-1,1]!=listing_panel[i,1]){
    xx <- 0
    listing_panel[i,4] <- xx
  }
}
d <- order(listing_panel[,"listing_id"],-listing_panel[,"month"])
listing_panel <- listing_panel[d,]
for(i in 2:nrow(listing_panel)){
  if(listing_panel[i,4]==0){
    listing_panel[i,4]=listing_panel[i-1,4]
  }
}
o <- order(listing_panel[,"listing_id"],listing_panel[,"month"])
listing_panel <- listing_panel[o,]
listing_0price <- listing_panel %>%
  filter(each_month_price == 0)
no_price <- unique(listing_0price$listing_id)

```

```{r drop NA listings, include=FALSE, echo = TRUE, message = FALSE, warning = FALSE}
#Filter data with no price
listing_panel <- listing_panel %>%
  filter(!listing_id %in% no_price)
```

## 1) Geographic Distribution

```{r plot the number of airbnb, fig.width=6.4, fig.height=6.0, include=TRUE, echo = TRUE, message = FALSE, warning = FALSE}
sf_use_s2(FALSE)
listings.sf<- listings %>% 
  st_as_sf(coords = c( "longitude","latitude"), crs = 4326, agr = "constant") %>% st_transform('ESRI:102013')

neighbor2 <- neighbor2 %>% 
  st_transform(st_crs(listings.sf))

listing.sf.neighbor2 <- st_intersection(listings.sf,neighbor2) %>% 
  dplyr::select(id, Buurt,Buurt_code) %>% 
  mutate(count=1) %>% 
  st_drop_geometry()

listings.sf <- left_join(listings.sf, listing.sf.neighbor2,by='id')

neighbo2.count <- listings.sf %>% 
  group_by(Buurt) %>%
  dplyr::summarise(airbnb.number = sum(count)) %>% 
  dplyr::select(Buurt, airbnb.number) %>% 
  st_drop_geometry()

neighbor2 <- left_join(neighbor2,neighbo2.count,by="Buurt")

ggplot()+
  geom_sf(data = neighbor2, aes(fill=q5(airbnb.number)),color='transparent')+
  scale_fill_manual(values = Pink,
                     labels = qBr(neighbor2,'airbnb.number'), name = 'Count')+
  labs(title = "Number of Airbnb per Neighborhood", subtitle = "Amsterdam, NL; 2018") +
  mapTheme()
```

```{r  fig.width=6.4, fig.height=6.0, include=TRUE, echo = TRUE, message = FALSE, warning = FALSE}


neighbor2 %>% ggplot() + 
      geom_sf(aes(fill = airbnb.number), color = 'white') +
      scale_fill_gradient(low = Purple[1], high = Purple[5],
                          name = "Count") +
      labs(title = "Number of Airbnb per Zipcode", subtitle = "Amsterdam, NL; 2018") +
      mapTheme()
```

Hotspots Fishnet

```{r Airbnb hotspot, fig.width=6.4, fig.height=6.0, include=TRUE, echo = TRUE, message = FALSE, warning = FALSE}
#create fishnet

amsterdam.boundary <- st_union(neighborhood) %>% st_transform('ESRI:102013')

fishnet <- 
  st_make_grid(amsterdam.boundary, cellsize = 300) %>%
    .[amsterdam.boundary] %>%
  st_sf() %>%
  mutate(uniqueID = rownames(.))

fishnet <- fishnet %>% 
  mutate(uniqueID = rownames(.))

fishnet.count <- st_intersection(listings.sf,fishnet) %>% 
  mutate(count = 1) %>% 
  st_drop_geometry() %>% 
  dplyr::select(uniqueID, count) %>% 
  group_by(uniqueID) %>% 
  summarise(countairbnb = sum(count))

airbnb_net <- 
  dplyr::select(listings.sf) %>% 
  mutate(countairbnb = 1) %>% 
  aggregate(., fishnet, sum)

airbnb_net <- airbnb_net %>% 
  mutate(countairbnb = tidyr::replace_na(countairbnb,0),
         uniqueID = row.names(.))

ggplot() +
  geom_sf(data = airbnb_net, aes(fill = countairbnb), color = NA) +
  scale_fill_viridis() +
  labs(title = "Count of airbnb for the fishnet") +
  mapTheme()
```

## 2) Price

### Seasonality

```{r price change, fig.width=8, fig.height=3.8, include = TRUE, echo=TRUE, warning= FALSE, message=FALSE}
Month_price <- calendar%>%
  mutate(date2 = ymd(date))%>%
  mutate(month = month(date2),
         listing_id = as.character(listing_id),
         price = parse_number(price))%>%
  mutate(month = as.character(month))%>%
  mutate(month = ifelse(month != 10 & month != 11 & month != 12, gsub("^","0",month), month)) %>%
  drop_na(price) %>%
  group_by(month) %>%
  dplyr::summarize(mean_monthly_price = mean(price))


ggplot(Month_price, 
       aes(x=month, y=mean_monthly_price, group =1)) +
  geom_line(size=1, color = Teal[3]) +
  labs(title = "Average Airbnb Price Every Month", subtitle = "Amsterdam, NL; 2018") +
  xlab("Month of the Year") + ylab("Average Price") +
  plotTheme()
```

### Price per Bed

```{r plot price per bed, fig.width=6.4, fig.height=6.0, include=TRUE, echo = TRUE, message = FALSE, warning = FALSE}
details.sf <- 
  details.sf %>% 
  mutate(priceBed=price/beds) %>% 
  filter(priceBed <=1000)


ggplot()+
  geom_sf(data = neighborhood,fill='grey95',color = 'white')+
  geom_sf(data = details.sf, aes(colour=q5(priceBed)),size=.5)+
  scale_color_manual(values = palette5,
                     labels = qBr(details.sf,'priceBed'), name="Price per Bed (Euro)") +
  labs(title = "Price per Bed",
       subtitle = 'Amsterdam Airbnb, price on 2018-12-6') +
  mapTheme()

```

## 3) Occupancy

```{r occupancy, fig.width=8, fig.height=3.8, include = TRUE, echo=TRUE, warning=FALSE, message=FALSE}
index <- function(x, flag = '0') {
  digit <- floor(log10(length(x))) + 1
  paste(flag, formatC(x, width = digit, flag = '0'), sep = '')
}

occupancy <- calendar%>%
  mutate(date2 = ymd(date))%>%
  mutate(month = month(date2),
         count = ifelse(available == "f", 1, 0),
         listing_id = as.character(listing_id))%>%
  filter(!listing_id %in% no_price) %>%
  group_by(listing_id, month) %>%
  dplyr::summarize(monthly_occupancy = sum(count))

monthly_occupancy <- occupancy %>%
  mutate(month = as.character(month))%>%
  mutate(month = ifelse(month != 10 & month != 11 & month != 12, gsub("^","0",month), month)) %>%
  group_by(month) %>%
  dplyr::summarise(mean_monthly_occupancy = mean(monthly_occupancy))

ggplot(monthly_occupancy, 
       aes(x=month, y=mean_monthly_occupancy, group =1)) +
  geom_line(size=1, color = "#FE9900") +
  labs(title = "Airbnb Occupancy Every Month", subtitle = "Amsterdam, NL; 2018") +
  xlab("Month of the Year") + ylab("Average Monthly Occupancy") +
  plotTheme()
```

## 4) Composition / Characteristics

### Room Layout

```{r basic features, include=TRUE, echo = TRUE, message = FALSE, warning = FALSE}

table.basic <- details.sf %>% 
  st_drop_geometry() %>% 
  dplyr::select(price ,beds, bedrooms, bathrooms, accommodates)

stargazer(as.data.frame(table.basic),
          type = "text",
          title ="Table 1. Basic Features Summary",
          single.row = TRUE,
          out.header = TRUE)

```

### Property Type

```{r}
count(details.sf$property_type) %>%
  kable() %>%
  kable_styling() 

```

### Puting them together...

```{r include=TRUE}

details.sf %>%
  st_drop_geometry() %>%
  group_by(beds, bathrooms, bedrooms, accommodates, property_type) %>%
  dplyr::summarize(Mean_Price = mean(price)) %>%
  kable() %>%
  kable_styling()

```

## 5) Amenities

```{r amenities, include=TRUE, echo = TRUE, message = FALSE, warning = FALSE}
#pool
details.sf <- details.sf %>%
  mutate(pool = ifelse(str_detect(amenities, "Pool"), "Yes", "No"))

#Paid parking off premises
details.sf <- details.sf %>%
  mutate(parking = ifelse(str_detect(amenities, "Paid parking off premises"), 
                          "Yes", "No"))

#Indoor fireplace
details.sf <- details.sf %>%
  mutate(fireplace = ifelse(str_detect(amenities, "Indoor fireplace"), 
                          "Yes", "No"))

#Waterfront
details.sf <- details.sf %>%
  mutate(waterfront = ifelse(str_detect(amenities, "Waterfront"), 
                          "Yes", "No"))

#Kitchen
details.sf <- details.sf %>%
  mutate(kitchen = ifelse(str_detect(amenities, "Kitchen"), 
                          "Yes", "No"))

#Air conditioning
details.sf <- details.sf %>%
  mutate(AC = ifelse(str_detect(amenities, "Air conditioning"), 
                          "Yes", "No"))
```

```{r plot amenities,fig.width=10, fig.height=6.8, include=TRUE, echo = TRUE, message = FALSE, warning = FALSE}
amenitie_vars <- c('fireplace','waterfront','pool','parking','kitchen','AC')
plotList <- list()

for (i in amenitie_vars){
plotList[[i]] <- 
  details.sf %>%st_drop_geometry() %>% 
  dplyr::select(price,i) %>%
  filter(price<500) %>% 
  gather(Variable, value, -price) %>%
    ggplot(aes(value, price, fill=value)) + 
      geom_boxplot() +
      scale_fill_manual(values = c("#FFDD94", "#CCABDB")) +
      labs(x="Amenity Status", y="Price",
           title = i) +
      theme(legend.position = "none") +
  plotTheme()
}

do.call(grid.arrange,c(plotList, ncol = 3, top = "Price w/ vs. w/o Amenities"))
```

### Aggregated Amenities:

In addition to each amenities listed above, we also included a feature named 'amenities.number' to explore the aggregated effect of amenities. Sometimes, regardless of specific types of amenities, simply the fact of having multiple amenities may increase the price visitors are willing to pay for an Airbnb.

```{r number of amenties listed, include=FALSE, echo = TRUE, message = FALSE, warning = FALSE}
library(stringr)

details.sf <- details.sf %>% 
  mutate(amenities.number = str_count(amenities,",")+1)

```

# New Features & Engineering

## New Feature 1: Spatial Lag & Neighborhood Effect

### Neighborhood Effect

```{r Neighborhood Effect, include=TRUE, echo = TRUE, message = FALSE, warning = FALSE }
details.sf.neighbor <- st_intersection(details.sf,zipcode4) %>% 
  dplyr::select(id, Postcode4) %>% 
  st_drop_geometry()

details.sf <- left_join(details.sf,details.sf.neighbor,by='id')

```

```{r neighbor effect2 , include=TRUE, echo = TRUE, message = FALSE, warning = FALSE}
neighbor2 <- neighbor2 %>% 
  st_transform(st_crs(listings.sf))

listing.sf.neighbor2 <- st_intersection(listings.sf,neighbor2) %>% 
  dplyr::select(id, Buurt,Buurt_code) %>% 
  mutate(count=1) %>% st_drop_geometry()

listing.sf.neighbor2$id <- as.character(listing.sf.neighbor2$id)

detail.sf <- left_join(details.sf,listing.sf.neighbor2, by = "id")
```

### Spatial Lag

```{r occupancy join, include=TRUE, echo = TRUE, message = FALSE, warning = FALSE}
occupancy3 <- occupancy %>%
  dplyr::rename(id = listing_id) 
  
occupancy3 <-  
  left_join(occupancy3, st_drop_geometry(details.sf), by = "id")
```

```{r price by month, include=TRUE, echo = TRUE, message = FALSE, warning = FALSE}
listing_panel <- listing_panel%>%
   dplyr::rename(id = listing_id)

revenue_panel <- merge(occupancy3,listing_panel[c("id","month","each_month_price")],by=c("id","month")) %>%
  mutate(revenue = each_month_price*monthly_occupancy)
```

```{r correlation matrix, include=TRUE, echo = TRUE, message = FALSE, warning = FALSE}

annualrevenue <- revenue_panel %>%
  group_by(id) %>%
  dplyr::summarise(annual_revenue = sum(revenue))


annualrevenue<- left_join(details.sf, annualrevenue,by="id")%>%
    filter(!id %in% no_price)%>%
    mutate(bathrooms = as.numeric(bathrooms),
         bedrooms = as.numeric(bedrooms))
```

```{r annual revenue spatial lag, include=TRUE, echo = TRUE, message = FALSE, warning = FALSE}

annualrevenue<- annualrevenue %>%
  drop_na(annual_revenue) %>%
  filter(annual_revenue <= 500000)

coords <- st_coordinates(annualrevenue) 

neighborList <- knn2nb(knearneigh(coords, 5))

spatialWeights <- nb2listw(neighborList, style="W")


annualrevenue$lagRevenue <- lag.listw(spatialWeights, annualrevenue$annual_revenue)

```

```{r annual revenue & spatial lag plot, include=TRUE, echo = TRUE, message = FALSE, warning = FALSE}
ggplot(annualrevenue)+
  geom_point(aes(x = lagRevenue, y = annual_revenue), alpha = 0.26)+
  geom_smooth(aes(x = lagRevenue, y =annual_revenue), method = "lm", se= FALSE, color = "orange")+
  labs(title="Annual Revenue as a function of lagRevenue", y='Annual Revenue', x = 'Lag Annual Revenue') +
  plotTheme()
```

## New Feature 2: Access to Public Transit

```{r}
listings$longitude = as.numeric(listings$longitude)
listings$latitude = as.numeric(listings$latitude)
listings.sf<- listings %>% 
  st_as_sf(coords = c( "longitude","latitude"), crs = 4326, agr = "constant")

st_crs(metro) <- st_crs(listings.sf)

st_c <- st_coordinates

details.sf.c <- details.sf%>%
  st_transform('ESRI:102013') %>%
  dplyr::select(geometry) %>%
  na.omit

metro.c <- metro%>%
  st_transform('ESRI:102013') 


```

```{r}
ggplot()+
  geom_sf(data = neighbor2, aes(fill=q5(airbnb.number)),color='transparent') +
  scale_fill_manual(values = Pink,
                     labels = qBr(neighbor2,'airbnb.number'), name = 'Count of Airbnb') +
  geom_sf(data=metro.c$geometry, aes(color=metro.c$Modaliteit)) +
  scale_color_manual(values=c(palette2[1], '#7171C6'), name = 'Type of Transit') +
  labs(title = "Public Transit & Number of Airbnb", subtitle = "Amsterdam, NL; 2018") +
  mapTheme()
```

```{r Metro Buffer}

#multi-ring buffer 
Metro_MRB <- multipleRingBuffer(st_union(metro.c), 6500, 500)

#USE FOR REG: MRB Spatial Join 
details.sf.c.MetroRings <-
  st_join(dplyr::select(details.sf.c, id),
          Metro_MRB) %>%
  st_drop_geometry() %>% 
  left_join(details.sf.c, #put the regression dataset here
            by="id") %>%
  st_sf()%>%
  mutate(metro.dist = distance/1000)

#Adding the variable to the data set
details.sf <- 
  left_join(details.sf, st_drop_geometry(dplyr::select(details.sf.c.MetroRings, distance, id)), by="id")%>%
  dplyr::rename(metro.dist = distance)
  
#FOR VIS ONLY: Creating a summary table of the ring data 
details.Rings.Summary <- details.sf.c.MetroRings %>%
  dplyr::select(metro.dist, price)%>%
  st_drop_geometry()%>%
  group_by(metro.dist)%>%
  dplyr::summarize(Price=median(price, na.rm=T))

#FOR VIS ONLY: Line Plot of the summary table 
ggplot(data=details.Rings.Summary, aes(x=distance, y=Price),)+
  geom_line(size=1.5)+
  geom_point(size = 3)+  
  labs(title = "Price as a Function of Distance from a Metro Station", 
       subtitle = "Amsterdam Airbnb Data, ", 
       x="Distance from a Metro Station (KM)",
       y="Rent (2018 USD)")+
  theme(plot.title = element_text(size=18))
```

## New Feature 3: Proximity to Tourist Amenities

# Feature Review: Correlation Matrix

```{r numeric correlation matrix, fig.width=6.4, fig.height=6.0, include=TRUE, echo = TRUE, message = FALSE, warning = FALSE}
numericVars <- 
  select_if(st_drop_geometry(annualrevenue), is.numeric) %>% na.omit() %>% 
  dplyr::select(annual_revenue,price,beds, bedrooms, bathrooms, 
                              minimum_nights,
                              amenities.number)

ggcorrplot(
  round(cor(numericVars), 1), 
  p.mat = cor_pmat(numericVars),
  colors = c("#4757a2", "white", "#E46B45"),
  type="lower",
  insig = "blank") +  
    labs(title = "Correlation across numeric variables") 
```

# Regression Model

## Data Split: Testing & Training

```{r annual revenue regression, include=TRUE, echo = TRUE, message = FALSE, warning = FALSE}
annualrevenue <- merge(annualrevenue,listing.sf.neighbor2[c("id", "Buurt")], by = "id")
```

```{r}
#Split training and test set
annualrevenue <- annualrevenue%>% st_drop_geometry()
set.seed(31497)

inTrain <- caret::createDataPartition(
  y =  paste(annualrevenue$Buurt),
  p = .6, list = FALSE)

annualrevenue.training <- st_drop_geometry(annualrevenue)[inTrain,]
annualrevenue.test     <- st_drop_geometry(annualrevenue)[-inTrain,]
```

## Regression Results

```{r}


#regression without distance thingy
reg.annualrevenue <- lm(price ~ ., data = st_drop_geometry(annualrevenue) %>% 
             dplyr::select(price, beds, bedrooms, bathrooms, accommodates,
                              pool, parking, kitchen, AC, fireplace,
                              room_type,property_type,bed_type, Buurt,
                              minimum_nights,
                              amenities.number,lagRevenue)) 

stargazer(reg.annualrevenue,
          type = "text",
          title ="Regression Output",
          single.row = TRUE,
          out.header = TRUE)

```

```{r annual revenue regression summ, include=TRUE, echo = TRUE, message = FALSE, warning = FALSE}

annualrev_predict_test <- annualrevenue.test %>%
  mutate(Prediction = predict(reg.annualrevenue, newdata = annualrevenue.test)) %>%
  mutate(Prediction = ifelse(Prediction > 0, Prediction, mean(annualrevenue.training$price)))%>%
  filter(price!=0)%>%
  drop_na(Prediction)%>%
  mutate(AE = abs(Prediction-price),
         APE = AE/Prediction)

test_result <- data.frame(MAE = c(mean(annualrev_predict_test$AE, na.rm=T)),
              MAPE = c(scales::percent(mean(annualrev_predict_test$APE, na.rm=T)))) 

test_result %>%
  kable(caption = "Figure 8. Mean absolute error and MAPE for a single test set")%>%
  kable_styling("striped", full_width = F)
```

```{r annual revenue regression plot, include=TRUE, echo = TRUE, message = FALSE, warning = FALSE}
ggplot(annualrev_predict_test,
         aes(x=APE)) + 
  labs(title = "APE Distribution",caption = "Figure XX. A histogram of APE") +
  geom_histogram()+
  plotTheme()
```

```{r}

ggplot(annualrev_predict_test %>%
        filter(APE<1.5),
         aes(x=APE)) + 
  labs(title = "APE Distribution",caption = "Figure XX. A histogram of APE") +
  geom_histogram()+
  plotTheme()
```

```{r  annual revenue regression plot by Buurt, include=TRUE, echo = TRUE, message = FALSE, warning = FALSE}
palette5 <- c("#ffffd4", "#fed98e", "#fe9929", "#d95f0e", "#993404")

annualrev_predict_test%>%
  group_by(Buurt) %>%
  dplyr::summarize(mean.APE = mean(APE, na.rm = T)) %>%
  ungroup() %>% 
  left_join(neighbor2,by = "Buurt") %>%
    st_sf() %>%
    ggplot() + 
      geom_sf(aes(fill = mean.APE),colour = 'transparent') +
      scale_fill_gradient(low = palette5[1], high = palette5[5],
                          name = "MAPE") +
      labs(title = "Average Test Set MAPE"
           #,subtitle = "2019"
           ) +
      mapTheme()

```

# Cross Validation: LOGO (Leave One Group Out)

```{r results='hide', message=FALSE, warning=FALSE}


reg.vars <- c("beds", "bedrooms", "bathrooms", "accommodates",
                              "pool", "parking", "kitchen", "AC", "fireplace",
                              "room_type",  "bed_type",
                              "amenities.number","lagRevenue")

airbnb.location <- details.sf %>% dplyr::select(id)

annualrev_predict_test <- annualrev_predict_test %>% left_join(airbnb.location, by='id')
colnames(annualrev_predict_test)[1] =  "identifier"

reg.spatialCV <- crossValidate(
  dataset = annualrev_predict_test,
  id = "Buurt",
  dependentVariable = "price",
  indVariables = reg.vars) %>%
    dplyr::select(identifier = Buurt, price, Prediction, geometry)

```

```{r message=FALSE, warning=FALSE}

reg.spatialCV <-
  reg.spatialCV %>%
  mutate(Error = Prediction - price)

error_by_reg_and_fold <-
  reg.spatialCV  %>%
  group_by(identifier) %>%
  dplyr::summarize(Mean_error = mean(Error, na.rm=T),
                   MAE = mean(abs(Mean_error), na.rm=T),
                   SD_MAE = mean(abs(Mean_error), na.rm=T)) %>%
  ungroup()

st_drop_geometry(error_by_reg_and_fold) %>%
    dplyr::summarize(Mean_MAE = round(mean(MAE), 2),
              SD_MAE = round(sd(MAE), 2)) %>%
  kable() %>%
    kable_styling("striped", full_width = F) 

```

```{r}

  ggplot() + 
  geom_sf(data=amsterdam.boundary, color='white') +
  geom_sf(data=error_by_reg_and_fold, aes(color=Mean_error)) +
  scale_color_gradient(low = '#91bfdb', high = '#fc8d59', name = "Mean Error") +
  labs(title = "Mean Error (LOGO-CV)", subtitle = "Amsterdam, NL") + mapTheme()

```

# Conclusion
